---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## stmprevalence: Inspect prevalence covariates

This package provides additional functionalities to examine the link between prevalence covariates and topic proportions. Namely, these are:

- Implementation of the method of composition, using either a quasibinomial GLM or a beta regression. The method of composition is implemented in the  [stm](http://www.structuraltopicmodel.com/) package through its function `stm::estimateEffect()`, employing a simple OLS regression. This violates the assumption of (sampled) topic proportions being restricted to `(0,1)`, which is the motivation for our extension.
- Direct assessment of the prevalence output produced by the stm, i.e. the MAP estimates for `Gamma` and `Sigma`, by sampling from a LogisticNormal distribution.

Both approaches can be used to visualize the empirical mean as well as credible intervals of topic proportions for the full observed range of a specified variable, while holding all other variables as mean/majority vote.

### Installation

You can install `stmprevalence` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("PMSchulze/stmprevalence")
```

### Examples
